Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Add modifications wrt previous commit.

\textbf{We show here how a multiple constraints solver works: its
  purpose is to find the root $q$ of a non-linear $C^1$ function
  $f(q)$ with a tolerance of $\varepsilon$. If we want to find a
  configuration on a manifold $\manifold$, $f(q)$ can be defined as a
  vector function that contains the concatenation of all constraints
  defining $\manifold$. Note that as the intersection of two or more
  manifolds is also a manifold, this multi-constraint solver allows us
  also to generate configurations that lie at the intersection of
  multiple manifolds.}

@@

The way we generate a goal configuration is the following:
\begin{enumerate}
\item \textbf{Shoot a random configuration $q_{rand}$ in $\mathcal{C}$ with
  uniform distribution.}
\item \textbf{Call \textit{constraint-solver}
  (Algorithm~\ref{algo:newton}) on $q_{rand}$, with the
  intersection of the planning and goal manifolds $\manifold \cap
  \goalmanifold$.}
\item If success, check for collisions.
\end{enumerate}

>>>>

\textbf{We show here how a multiple constraints solver works: its
  purpose is to find the root $q$ of a non-linear $C^1$ function
  $f(q)$ with a tolerance of $\varepsilon$. If we want to find a
  configuration on a manifold $\manifold$, $f(q)$ can be defined as a
  vector function that contains the concatenation of all constraints
  defining $\manifold$. Note that as the intersection of two or more
  manifolds is also a manifold, this multi-constraint solver allows us
  also to generate configurations that lie at the intersection of
  several manifolds.}

@@

The way we generate a goal configuration is the following:
\begin{enumerate}
\item \textbf{Shoot a random configuration $q_{rand}$ in $\mathcal{C}$ with
  uniform distribution.}
\item \textbf{Call \textit{constraint-solver}
  (Algorithm~\ref{algo:newton}) on $q_{rand}$, with $f(q)$ defined by
  the intersection of the planning and goal manifolds $\manifold \cap
  \goalmanifold$.}
\item If success, check for collisions.
\end{enumerate}
